---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# lave

The goal of the `lave` package is to provide an extensible deparsing function for R.
Like `base::deparse()` and others, the output is intended to produce results that are (almost) identical to the input when evaluated.
Unlike the `base` equivalents, `lave` aims at making the output as human-friendly as possible.

The `lave()` function is rougly equivalent to `deparse()`, but with nicer defaults.
The `lavec()` function returns an object which can be passed to `eval()` but also retains the desired formatting---a better `dput()`.


## Examples

```{r echo=FALSE, message=FALSE}
devtools::load_all()
```

```{r}
lave(1)
lavec(1L)
lavec(Sys.time())
lavec(print)

eval(lavec(print))
```

Compare this to the `dput()` output:

```{r}
deparse(1)
dput(1L)
dput(Sys.time())
dput(print)

eval(parse(text = deparse(print)))
```


## Installation

Install via

```r
devtools::install_github("krlmlr/lave")
```
