---
title: "Pretty calls"
author: "Kirill Müller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pretty calls}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The default `print()` method prints the source if available (from a srcref attribute) for expression objects, but not for calls. See below for an example (run in R 3.3.1).

It looks like this change has been introduced in R 2.10.0, in [revision r48366](https://github.com/wch/r-source/commit/107f16133e3db7#diff-12de104c9320556f0e99da345c6fb259L650) [2], but it hasn't been documented explicitly. I'm wondering if calls should use an attached srcref for printing. For now, `lave` uses the class `"srcref_call"` with an overridden `print()` method.


## Construct and parse a simple call

```{r }
text <- "a(\n)"
text

ex <- parse(text = text, srcfile = srcfilecopy("dump.R", text))
```

Returns an "expression", it uses the srcref for printing

```{r }
ex
attributes(ex)
```

## Extract the call, attach srcref attributes

```{r }
cl <- ex[[1]]
attr(cl, "srcref") <- attr(ex, "srcref")[[1]]
attr(cl, "srcfile") <- attr(ex, "srcfile")
attr(cl, "wholeSrcref") <- attr(ex, "wholeSrcref")
```

The call does *not* use the srcref for printing

```{r }
cl
```

## Hack around it

```{r }
print.call <- function(x, ..., useSource = TRUE) {
  print(attr(x, "wholeSrcref"), ...)
}
```

Now works as expected

```{r }
print(cl)
```
